\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\title{Test Report with References}
\author{Test Author}
\date{\today}

\begin{document}

\maketitle

\tableofcontents

\section{Introduction}
\label{sec:introduction}

This is the introduction section. We will discuss various topics in this document.

As mentioned in Section~\ref{sec:methodology}, our approach is comprehensive.
The results are presented in Section~\ref{sec:results}.

\section{Methodology}
\label{sec:methodology}

This section describes the methodology used in our research.

We refer back to the concepts introduced in Section~\ref{sec:introduction}.
The detailed analysis can be found in Section~\ref{sec:analysis}.

\section{Results}
\label{sec:results}

Here are the main results of our study.

For more context, see Section~\ref{sec:introduction} and Section~\ref{sec:methodology}.

\section{Analysis}
\label{sec:analysis}

This section provides detailed analysis of the results from Section~\ref{sec:results}.

The methodology described in Section~\ref{sec:methodology} supports these findings.

\section{Discussion}
\label{sec:discussion}

This section discusses the implications of our findings from Section~\ref{sec:results}.

The analysis in Section~\ref{sec:analysis} provides the foundation for these discussions.

\section{Conclusion}
\label{sec:conclusion}

In conclusion, this document has demonstrated that section references work correctly:
\begin{itemize}
    \item Introduction (Section~\ref{sec:introduction})
    \item Methodology (Section~\ref{sec:methodology})
    \item Results (Section~\ref{sec:results})
    \item Analysis (Section~\ref{sec:analysis})
    \item Discussion (Section~\ref{sec:discussion})
\end{itemize}

The LaTeX compilation handles cross-references properly, ensuring that all references like Section~\ref{sec:introduction} and Section~\ref{sec:methodology} are resolved correctly instead of showing "???" marks.

\end{document} 